---
#########################################
# options for knitting a single chapter #
#########################################
output:
  bookdown::html_document2: default
  bookdown::word_document2: default
  bookdown::pdf_document2:
    template: templates/brief_template.tex
documentclass: book
bibliography: references.bib
---


# Methods and data

```{r setup2, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(knitr)
```

## Subsection title

Write one sentence per line.
Leave one blank line to separate paragraphs. 
Write one sentence per line.
Leave one blank line to separate paragraphs.
Write one sentence per line.
Leave one blank line to separate paragraphs.


Consider a variable, $y_{it}$, that can be decomposed as follows:

\begin{equation}
y_{it}=g_{it}+a_{it}
\end{equation}
where $g_{it}$ is a systematic component and $a_{it}$ is a transitory component.
To further separate common from idiosyncratic components, we could apply 

$$y_{it}=\left(\frac{g_{it}+a_{it}}{\mu_{t}}\right)\mu_{t}=\delta_{it}\mu_{t}$$
where $\delta_{it}$ is an idiosyncratic component and $\mu_{t}$ is a common component.


Write one sentence per line.
Leave one blank line to separate paragraphs. 
Write one sentence per line.
Leave one blank line to separate paragraphs.
Write one sentence per line.
Leave one blank line to separate paragraphs.

Write one sentence per line.
Leave one blank line to separate paragraphs. 
Write one sentence per line.
Leave one blank line to separate paragraphs.
Write one sentence per line.
Leave one blank line to separate paragraphs.

You can cite in this way[@Shea2014; @Lottridge2012].
Or this other way. @Shea2014 and @Lottridge2012 found that ...

Write one sentence per line.
Leave one blank line to separate paragraphs. 
Write one sentence per line.
Leave one blank line to separate paragraphs.
Write one sentence per line.
Leave one blank line to separate paragraphs.

here's a plot created in R

```{r codeChunkName, fig.cap="Title of the figure", out.width="70%", fig.align='center'}
ggplot(cars) +
  aes(x = speed, y = dist) +
  geom_point()
```
Write one sentence per line.
Leave one blank line to separate paragraphs. 
Write one sentence per line.
Leave one blank line to separate paragraphs.
Write one sentence per line.
Leave one blank line to separate paragraphs.

Write one sentence per line.
Leave one blank line to separate paragraphs. 
Write one sentence per line.
Leave one blank line to separate paragraphs.
Write one sentence per line.
Leave one blank line to separate paragraphs.

## Section title

Write one sentence per line.
Leave one blank line to separate paragraphs. 
Write one sentence per line.
Leave one blank line to separate paragraphs.
Write one sentence per line.
Leave one blank line to separate paragraphs.

Write one sentence per line.
Leave one blank line to separate paragraphs. 
Write one sentence per line.
Leave one blank line to separate paragraphs.
Write one sentence per line.
Leave one blank line to separate paragraphs


A nice table

```{r}
cars %>% 
  head(5) %>% 
  kable(caption = "A knitr kable table") 
```


## Section title
