---
title: "Regressions tables from stargazer"
author: "Carlos Mendez"
date: "5/29/2020"
output:
  html_document: default
  pdf_document:
    includes:
      in_header: "preamble.tex"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  cache=TRUE,
  messages=FALSE,
  warning=FALSE,
  out.width = "95%")
library(tidyverse)
library(knitr)
options(digits = 3)
options(scipen = 999)
options(kableExtra.auto_format = FALSE) 
library(kableExtra)
library(xtable)
library(stargazer)
```


## Descriptive statistics

### Latex

```{r }
stargazer(attitude)
```


\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\ 
\hline \\[-1.8ex] 
rating & 30 & 64.600 & 12.200 & 40 & 58.8 & 71.8 & 85 \\ 
complaints & 30 & 66.600 & 13.300 & 37 & 58.5 & 77 & 90 \\ 
privileges & 30 & 53.100 & 12.200 & 30 & 45 & 62.5 & 83 \\ 
learning & 30 & 56.400 & 11.700 & 34 & 47 & 66.8 & 75 \\ 
raises & 30 & 64.600 & 10.400 & 43 & 58.2 & 71 & 88 \\ 
critical & 30 & 74.800 & 9.890 & 49 & 69.2 & 80 & 92 \\ 
advance & 30 & 42.900 & 10.300 & 25 & 35 & 47.8 & 72 \\ 
high.rating & 30 & 0.333 & 0.479 & 0 & 0 & 1 & 1 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table} 




## Regression models


### Latex

```{r }
## 2 OLS models
linear.1 <- lm(rating ~ complaints + privileges + learning + raises + critical, data=attitude)
linear.2 <- lm(rating ~ complaints + privileges + learning, data=attitude)
 
## create an indicator dependent variable, and run a probit model
 
attitude$high.rating <- (attitude$rating > 70)
probit.model <- glm(high.rating ~ learning + critical + advance, data=attitude, family = binomial(link = "probit"))
 
stargazer(linear.1, linear.2, probit.model, title="Regression Results", align=TRUE)
```

\begin{table}[!htbp] \centering 
  \caption{Regression Results} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
\cline{2-4} 
\\[-1.8ex] & \multicolumn{2}{c}{rating} & \multicolumn{1}{c}{high.rating} \\ 
\\[-1.8ex] & \multicolumn{2}{c}{\textit{OLS}} & \multicolumn{1}{c}{\textit{probit}} \\ 
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)}\\ 
\hline \\[-1.8ex] 
 complaints & 0.692^{***} & 0.682^{***} &  \\ 
  & (0.149) & (0.129) &  \\ 
  & & & \\ 
 privileges & -0.104 & -0.103 &  \\ 
  & (0.135) & (0.129) &  \\ 
  & & & \\ 
 learning & 0.249 & 0.238^{*} & 0.164^{***} \\ 
  & (0.160) & (0.139) & (0.053) \\ 
  & & & \\ 
 raises & -0.033 &  &  \\ 
  & (0.202) &  &  \\ 
  & & & \\ 
 critical & 0.015 &  & -0.001 \\ 
  & (0.147) &  & (0.044) \\ 
  & & & \\ 
 advance &  &  & -0.062 \\ 
  &  &  & (0.042) \\ 
  & & & \\ 
 Constant & 11.000 & 11.300 & -7.480^{**} \\ 
  & (11.700) & (7.320) & (3.570) \\ 
  & & & \\ 
\hline \\[-1.8ex] 
Observations & \multicolumn{1}{c}{30} & \multicolumn{1}{c}{30} & \multicolumn{1}{c}{30} \\ 
R$^{2}$ & \multicolumn{1}{c}{0.715} & \multicolumn{1}{c}{0.715} &  \\ 
Adjusted R$^{2}$ & \multicolumn{1}{c}{0.656} & \multicolumn{1}{c}{0.682} &  \\ 
Log Likelihood &  &  & \multicolumn{1}{c}{-9.090} \\ 
Akaike Inf. Crit. &  &  & \multicolumn{1}{c}{26.200} \\ 
Residual Std. Error & \multicolumn{1}{c}{7.140 (df = 24)} & \multicolumn{1}{c}{6.860 (df = 26)} &  \\ 
F Statistic & \multicolumn{1}{c}{12.100$^{***}$ (df = 5; 24)} & \multicolumn{1}{c}{21.700$^{***}$ (df = 3; 26)} &  \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 

### Latex with longer names 

```{r}
stargazer(linear.1, linear.2, probit.model, title="Regression Results", align=TRUE, dep.var.labels=c("Overall Rating","High Rating"), covariate.labels=c("Handling of Complaints","No Special Privileges", "Opportunity to Learn","Performance-Based Raises","Too Critical","Advancement"), omit.stat=c("LL","ser","f"), no.space=TRUE)
```


\begin{table}[!htbp] \centering 
  \caption{Regression Results} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
\cline{2-4} 
\\[-1.8ex] & \multicolumn{2}{c}{Overall Rating} & \multicolumn{1}{c}{High Rating} \\ 
\\[-1.8ex] & \multicolumn{2}{c}{\textit{OLS}} & \multicolumn{1}{c}{\textit{probit}} \\ 
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)}\\ 
\hline \\[-1.8ex] 
 Handling of Complaints & 0.692^{***} & 0.682^{***} &  \\ 
  & (0.149) & (0.129) &  \\ 
  No Special Privileges & -0.104 & -0.103 &  \\ 
  & (0.135) & (0.129) &  \\ 
  Opportunity to Learn & 0.249 & 0.238^{*} & 0.164^{***} \\ 
  & (0.160) & (0.139) & (0.053) \\ 
  Performance-Based Raises & -0.033 &  &  \\ 
  & (0.202) &  &  \\ 
  Too Critical & 0.015 &  & -0.001 \\ 
  & (0.147) &  & (0.044) \\ 
  Advancement &  &  & -0.062 \\ 
  &  &  & (0.042) \\ 
  Constant & 11.000 & 11.300 & -7.480^{**} \\ 
  & (11.700) & (7.320) & (3.570) \\ 
 \hline \\[-1.8ex] 
Observations & \multicolumn{1}{c}{30} & \multicolumn{1}{c}{30} & \multicolumn{1}{c}{30} \\ 
R$^{2}$ & \multicolumn{1}{c}{0.715} & \multicolumn{1}{c}{0.715} &  \\ 
Adjusted R$^{2}$ & \multicolumn{1}{c}{0.656} & \multicolumn{1}{c}{0.682} &  \\ 
Akaike Inf. Crit. &  &  & \multicolumn{1}{c}{26.200} \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 


### Text

```{r}
stargazer(linear.1, linear.2, probit.model, type="text", title="Regression Results", align=TRUE)
```

### Text

```{r}
stargazer(linear.1, linear.2, probit.model, type="html", title="Regression Results", align=TRUE)
```

### HTML 

```{r, results= "asis"}
stargazer(linear.1, linear.2, probit.model, type="html", title="Regression Results", align=TRUE)
```

