---
title: "Productivity dynamics across 26 provinces in Indonesia 1990-2010:"
subtitle: "An interactive and automated exploration in R"
author: "Carlos Mendez and Mitsuhiko Kataoka"
output:
  html_document:
    code_download: true
    df_print: paged
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 4
    number_sections: true
    code_folding: "show"
    theme: "cosmo"
    highlight: "monochrome"
  pdf_document: default
  word_document: default
---

<style>
h1.title {font-size: 18pt; color: DarkBlue;} 
body, h1, h2, h3, h4 {font-family: "Palatino", serif;}
body {font-size: 12pt;}
/* Headers */
h1,h2,h3,h4,h5,h6{font-size: 14pt; color: #00008B;}
body {color: #333333;}
a, a:hover {color: #8B3A62;}
pre {font-size: 12px;}
</style>


```{r setup, include=F}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
#library(rio)           # import stata files
library(ExPanDaR)      # explore panel data interactively
library(kableExtra)    # nicer tables
library(DT)            # interactive tables
#library(pmdplyr)       # managing panel and hierarchical data
library(panelr)        # managing panel  data
library(skimr)         # descriptive statistics
#library(gganimate)     # animated figures
library(plotly)        # interactive figures
#library(countrycode)   # add continent name
theme_set(theme_minimal())

# Change the presentation of decimal numbers to 4 and avoid scientific notation
options(prompt="R> ", digits=4, scipen=999)
```


Suggested citation: 

> Mendez, C. and Kataoka, M. (2020). Productivity dynamics across 26 provinces in Indonesia 1990-2010:: An interactive and automated exploration in R. R Studio/RPubs. Available at <https://rpubs.com/quarcs-lab/data-indonesia-26provinces-1990-2010>

This work is licensed under the Creative Commons Attribution-Share Alike 4.0 International License. 



# Original data source

The data are taken from ... [TBA]

```{r}
dat <- read_csv("../data/rawData/Data_JR_Mendez.csv")
dat
```

```{r}
str(dat)
```


# Generate additional variables

## Labor productivity

```{r}
dat <- dat %>% 
  mutate(
    lp = Y/L
  )
```

## Physical capital per worker

```{r}
dat <- dat %>% 
  mutate(
    k = K/L
  )
```

## Physical capital to Output ratio

```{r}
dat <- dat %>% 
  mutate(
    ky = K/Y
  )
```

## Human capital per worker

```{r}
# H was already per worker, so just use lower case
dat <- dat %>% 
  mutate(
    H = H*L
  ) %>% 
  mutate(
    h = H/L
  )
```

## Aggregate efficiency (parametric)

```{r}
dat <- dat %>% 
  mutate(
    tfp = Y/(((K^0.33)*((h*L)^(1-0.33))))
  )
```


## Aggregate efficiency (non-parametric)

```{r}
dat <- dat %>% 
  mutate(
    oe100 = oe*100
  )
```


# Select variables


```{r}
dat <- dat %>% 
  select(
    province,
    year,
    lp,
    k,
    ky,
    h,
    tfp,
    oe100
  )
```

```{r}
str(dat)
```


# Generate log variables

```{r}
dat <- dat %>% 
  mutate(
    log_lp = log(lp),
    log_k  = log(k),
    log_ky = log(ky),
    log_h  = log(h),
    log_tfp = log(tfp),
    log_oe100 = log(oe100)
  )
```



# Descriptive statistics

```{r}
dat %>% 
  mutate(year = as.character(year)) %>% 
  filter(year == 1990) %>% 
  select(-province, -year) %>% 
skim() %>% 
  kable() %>% 
  kable_styling()

```

```{r}
dat %>% 
  mutate(year = as.character(year)) %>% 
  filter(year == 2010) %>% 
  select(-province, -year) %>% 
skim() %>% 
  kable() %>% 
  kable_styling()
```



# Definitions of variables


## Show definitions of variables

```{r}
df_definitions <- read_csv("../data/code01-R-explore-dataset_df_def.csv") 
df_definitions
```



# Interactive Table


```{r}
# Define function for  interactive table
create_dt <- function(x){
  DT::datatable(x,
                extensions = 'Buttons',
                options = list(dom = 'Blfrtip',
                               buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                               lengthMenu = list(c(10,25,50,-1),
                                                 c(10,25,50,"All"))))
}
```




```{r}
dat %>% 
  create_dt() %>% 
  formatRound(columns =c(
"lp",                    
"k",                     
"h",                     
"tfp",                   
"oe100",                 
"log_lp",                
"log_k",
"log_ky",
"log_h",                 
"log_tfp",               
"log_oe100"
  ),
  digits = 2)

```


# Export data

```{r}
write_csv(dat, "../data/code01-R-explore-dataset.csv")
```


# Interactive and Automated exploration


- Initial exploration


```{r eval=FALSE, include=T}
# Run it in the console

ExPanD(
  df = dat,
  df_def = df_definitions,
  export_nb_option = TRUE,
  title = "TBA",
  abstract = paste("TBA")
    )

```



- Automated exploration: First you customize the exploration, export configuration file, and include it in the new set up of the exploration.


```{r}
config_list_fromRDS <- readRDS("ExPanD.RDS")
```


```{r eval=FALSE, include=FALSE}
# Run it in the console

ExPanD(
  df = dat,
  df_def = df_definitions,
  export_nb_option = TRUE,
  config_list = config_list_fromRDS,
  title = "TBA",
  abstract = paste("TBA")
    )

```



- Interactive Dashborad (Shiny Web App)

(TO be added later)

> <>



# References





END




