---
title: "Data exploration"
subtitle: "An interactive and automated exploration in R"
author: "Carlos Mendez"
output:
  html_document:
    code_download: true
    df_print: paged
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 4
    number_sections: true
    code_folding: "show"
    theme: "cosmo"
    highlight: "monochrome"
  pdf_document: default
  word_document: default
---

<style>
h1.title {font-size: 18pt; color: DarkBlue;} 
body, h1, h2, h3, h4 {font-family: "Palatino", serif;}
body {font-size: 12pt;}
/* Headers */
h1,h2,h3,h4,h5,h6{font-size: 14pt; color: #00008B;}
body {color: #333333;}
a, a:hover {color: #8B3A62;}
pre {font-size: 12px;}
</style>


```{r setup, include=F}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(ExPanDaR) 

theme_set(theme_minimal())

# Change the presentation of decimal numbers to 4 and avoid scientific notation
options(prompt="R> ", digits=4, scipen=999)
```



>  Available at <https://carlosmendez777.shinyapps.io/ehc1990and2016/>

This work is licensed under the Creative Commons Attribution-Share Alike 4.0 International License. 



# Original data source

The data are taken from ... [TBA]


# Import the data

```{r}
dat <- read_csv("../data/dataLong2years-geo-iso.csv")
dat
```

```{r}
glimpse(dat)
```

Select all variables but id

```{r}
dat <- dat %>% 
  select(
    -id
  )
```



# Definitions of variables


```{r}
df_definitions <- read_csv("../data/definitions.csv")
df_definitions 
```


Remove the first raw

```{r}
df_definitions = df_definitions[-1,]
df_definitions
```

# Interactive exploration

## Initial exploration

```{r eval=FALSE, include=T}
# Run it in the console
ExPanD(
  df = dat,
  df_def = df_definitions,
  export_nb_option = TRUE,
  title = "Automatic data exploration",
  abstract = paste("TBA")
    )
```


## Customized exploration

```{r}
customized <- readRDS("ExPanD.RDS")
```



```{r eval=FALSE, include=T}
# Run it in the console
ExPanD(
  df = dat,
  df_def = df_definitions,
  config_list = customized,
  export_nb_option = TRUE,
  title = "Data exploration of expected human capital",
  abstract = paste("Work in progress")
    )
```



END




