---
title: "Descriptive statistics from stargazer"
author: "Carlos Mendez"
date: "5/29/2020"
output:
  github_document: default
  pdf_document:
    includes:
      in_header: preamble.tex
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  cache=TRUE,
  messages=FALSE,
  warning=FALSE,
  out.width = "95%")
library(tidyverse)
library(knitr)
options(digits = 2)
options(scipen = 999)
options(kableExtra.auto_format = FALSE) 
library(kableExtra)
library(xtable)
library(stargazer)
```


## The data: attitude {datasets}

Default R data

From a survey of the clerical employees of a large financial organization, the data are aggregated from the questionnaires of the approximately 35 employees for each of 30 (randomly selected) departments. The numbers give the percent proportion of favourable responses to seven questions in each department.

A data frame with 30 observations on 7 variables. The first column are the short names from the reference, the second one the variable names in the data frame:

Y	rating	numeric	Overall rating
X[1]	complaints	numeric	Handling of employee complaints
X[2]	privileges	numeric	Does not allow special privileges
X[3]	learning	numeric	Opportunity to learn
X[4]	raises	numeric	Raises based on performance
X[5]	critical	numeric	Too critical
X[6]	advancel	numeric	Advancement


```{r}
df <- attitude
```


```{r}
df
```


```{r}
df %>% 
  glimpse()
```



## Descriptive statistics

### Latex

```{r }
stargazer(attitude,
          covariate.labels=c("The Rating",
                   "Handling of Complaints",
                   "No Special Privileges",
                   "Opportunity to Learn",
                   "Performance-Based Raises",
                   "Too Critical",
                   "Advancement",
                   "Very High Rating"),
          title="Descriptive statistics",
          notes = "Notes: Here are some notes",
          median = TRUE,
          iqr = FALSE,
          digits = 2,
          align = TRUE,
          type = "text",
          no.space = TRUE,
          out = "../results/tab-descriptiveStats.tex")
```





## Regression models

```{r}
## 2 OLS models
linear.1 <- lm(rating ~ complaints + privileges + learning + raises + critical, data=attitude)
linear.2 <- lm(rating ~ complaints + privileges + learning, data=attitude)
 
## create an indicator dependent variable, and run a probit model
 
attitude$high.rating <- (attitude$rating > 70)
probit.model <- glm(high.rating ~ learning + critical + advance, data=attitude, family = binomial(link = "probit"))
```




### Text

```{r}
stargazer(linear.1, linear.2, probit.model, type="text", title="Regression Results", align=TRUE)
```




### Latex

```{r }
stargazer(linear.1, linear.2, probit.model, title="Regression Results", align=TRUE)
```



### Latex with longer names 

```{r}
stargazer(linear.1, linear.2, probit.model, title="Regression Results", align=TRUE, dep.var.labels=c("Overall Rating","High Rating"), covariate.labels=c("Handling of Complaints","No Special Privileges", "Opportunity to Learn","Performance-Based Raises","Too Critical","Advancement"), omit.stat=c("LL","ser","f"), no.space=TRUE)
```


### HTML 

```{r, results= "asis"}
stargazer(linear.1, linear.2, probit.model, type="html", title="Regression Results", align=TRUE)
```

### Export latex table

```{r, results= "asis"}
stargazer(linear.1, linear.2, probit.model,
          title="Regression Results",
          align=TRUE,
          type = "html",
          no.space = TRUE,
          out = "../results/table.tex")
```


### Export html table


```{r}
stargazer(linear.1, linear.2, probit.model,
          title="Regression Results",
          align=TRUE,
          type = "text",
          no.space = TRUE,
          out = "../results/table.html")
```


### Export text table


```{r}
stargazer(linear.1, linear.2, probit.model,
          title="Regression Results",
          align=TRUE,
          type = "text",
          no.space = TRUE,
          out = "table.text")
```


## Input external tables

### From latex code

<!-- To compile to pdf add the following:  \input{table.tex} -->



## Word tables

```{r eval=T, echo=FALSE}
stargazer(linear.1, linear.2, probit.model,
          title="Regression Results",
          align=TRUE,
          type = "text",
          no.space = TRUE,
          out = "table.text")
```



